Dynamical Properties of Molecular Gas Complexes in a Redshift 6 Prototypical Galaxy at the Epoch of Reionization

### 2018-08-13 WRITEUP/ms.tex
add some figures

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16_alphavir.png}  
\caption{
Virial parameter and cloud mass of \flower of a given snapshot (accreting phase).
\label{fig:alpha16}}
\end{figure*}

>>>>

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16_alphavir.png}  
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16_PVE.png}
\caption{
Top: Virial parameter and cloud mass of \flower of a given snapshot (accreting phase).
Bottom: $\sigma^2/R - \Sigma_{\rm gas}$ relation of MCs in the same snapshot.
\label{fig:alpha16}}
\end{figure*}

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss27_alphavir.png}  
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss27_PVE.png}
\caption{
Top: Virial parameter and cloud mass of \flower of a given snapshot (starburst phase).
Bottom: $\sigma^2/R - \Sigma_{\rm gas}$ relation of MCs in the same snapshot.
\label{fig:alpha27}}
\end{figure*}

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16_larsons.png}  
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss27_larsons.png}  
\caption{
Larson's relation of \flower in 
accreting phase (top) and
starburst phase(bottom) and 
those observed in nearby and the \z$\sim$2 star-forming galaxy.
\label{fig:larsons_single}}
\end{figure*}

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16-28_alphavir.png}  
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16-28_PVE.png}
\caption{
Top: Virial parameter and cloud mass of MCs in \flower identified across all snapshots.
Bottom: $\sigma^2/R - \Sigma_{\rm gas}$ relation of MCs.
\label{fig:alpha16-28}}
\end{figure*}

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16-28_larsons.png}  
\caption{
Larson's relation of \flower across all snapshots (showing MC properties in different evolutionary 
phases) and 
those observed in nearby and the \z$\sim$2 star-forming galaxy.
\label{fig:larsons16-28}}
\end{figure*}

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16-28-alphavir-highncut.png}
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16-28-PVE-highncut.png}
\caption{
Same as \Fig{alpha16-28}, but MCs here are those identified from the highest $n_{\rm cut}$,
where only denser substructures of the main disk of \flower are included. 
\label{fig:alpha16-28-highncut}}
\end{figure*}

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16-28-larsons-highncut.png}  
\caption{
Same as \Fig{larsons16-28}, but MCs here are those identified from the highest $n_{\rm cut}$,
where only denser substructures of the main disk of \flower are included. 
\label{fig:larsons16-28-highncut}}
\end{figure*}
